Tampering Detection In Low-Power Smart Cameras

### 2015-05-28 paper.tex
Inserito criterio di calinski abracadabra

The initial number of clusters is instead chosen by \gi{aggiungere reeference e dire che è una procedura iterativa in cui abbiamo inserito il kmeans peasato.}

>>>>

The number of clusters is instead chosen by the Calinski-Harabasz criterion~\cite{calinski1974dendrite}, which considers different k-means instances with different number of clusters, and chooses the best one using a cost function. \ad{which is an iterative procedure where we put weighted k-means}.\gi{aggiungere reeference e dire che è una procedura iterativa in cui abbiamo inserito il kmeans peasato.}
